О множествах точек на плоскости с целочисленными расстояниями

### 2019-05-09 pps-linear-bound/pps-linear-lower-bound.tex
Linguistic issues

\paragraph{Abstract.}
A point set $M$ in $m$-dimensional Euclidean space is called an integral point set if all the distances between the
elements of $M$ are integers and $M$ is not situated on an $(m-1)$-dimensional hyperplane.
We improve the linear lower bound for planar integral point sets.
This bound involves facts related to the Point Packing in a Square problem.
Then for arbitrary integers $m \geq 2$, $n \geq m+1$, $d \geq 1$
we give a construction of an integral point set $M$ of $n$ points in $m$-dimensional Euclidean space
where $M$ contains points $M_1$ and $M_2$ such that distance between $M_1$ and $M_2$ is exactly $d$.

@@

For $m \geq 3$, hypothesis 3.1 can be easily proved:
indeed, we can just take a facher integral point set acording to construction 1
with sufficiently large height and then apply the ``blowing up'' procedure described in~\cite[theorem 1.3]{kurz2008bounds},
replacing the out-of-line point with an $(m-2)$-dimensional simplex with proper side length.
That simplex will consist of $m-1$ points;
we can throw out up to all the points $M_J$ and still have points $H_{1,2}$ with distance 1.
So, the set consists of $m+1$ or more points and has distance 1 occuring in it.
As distance 1 occurs in the obtained set, it is irreducible.

@@

\section{Acknowledgements}
Author thanks Prof. E.M. Semenov for the fruitful discussion and ideas
and A.S. Chervinskaia for the idea of using the term ``facher''.

>>>>

\paragraph{Abstract.}
A point set $M$ in $m$-dimensional Euclidean space is called an integral point set if all the distances between the
elements of $M$ are integers and $M$ is not situated on an $(m-1)$-dimensional hyperplane.
We improve the linear lower bound for planar integral point sets.
This improvement takes into account some results related to the Point Packing in a Square problem.
Then for arbitrary integers $m \geq 2$, $n \geq m+1$, $d \geq 1$
we give a construction of an integral point set $M$ of $n$ points in $m$-dimensional Euclidean space
where $M$ contains points $M_1$ and $M_2$ such that distance between $M_1$ and $M_2$ is exactly $d$.

@@

For $m \geq 3$, hypothesis 3.1 can be easily proved:
indeed, we can just take a facher integral point set according to construction 1
with sufficiently large height and then apply the ``blowing up'' procedure described in~\cite[theorem 1.3]{kurz2008bounds},
replacing the out-of-line point with an $(m-2)$-dimensional simplex with proper side length.
That simplex will consist of $m-1$ points;
we can throw out up to all the points $M_J$ and still have points $H_{1,2}$ with distance 1.
So, the set consists of $m+1$ or more points and has distance 1 occuring in it.
As distance 1 occurs in the obtained set, it is irreducible.

@@

\section{Acknowledgements}
Author thanks Prof. E.M. Semenov for the fruitful discussion and ideas
and A.S. Chervinskaia for the idea of using the term ``facher'' and other linguistic advices.
